Analysis

### 2017-04-12 Analysis.Rmd
Update analysis file with links and instruction for interpretation

>>>>

#### How to interpret these analyses

For a quick overview, see this thread on Stack Overflow that walks through the output of `summary.MCMCglmm`,
which is used below. [R: Making sense of the output of a MCMCglmm](http://stackoverflow.com/questions/20993643/r-making-sense-of-the-output-of-a-mcmcglmm)

The MCMCglmm documentation is more in-depth but should still be referenced.
```{r, eval=FALSE}
library(MCMCglmm)
vignette("Overview")
vignette("CourseNotes")
```
